---
title: "Assignment: Assignment 6"
author: Kaylar Fullington
date: 2/6/2022
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```

## Set the working directory to the root of your DSC 520 directory
setwd("C:/Users/runek/dsc520")

## Load the `data/r4ds/heights.csv` to
heights_df <- read.csv("data/r4ds/heights.csv")
```{r echo = FALSE}
heights_df <- read.csv("data/r4ds/heights.csv")
```

## Load the ggplot2 library
library(ggplot2)
```{r echo = FALSE}
library(ggplot2)
```

## Fit a linear model using the `age` variable as the predictor and `earn` as the outcome
age_lm <- lm(earn ~ age, data = heights_df)
```{r echo = FALSE}
age_lm <- lm(earn ~ age, data = heights_df)
```

## View the summary of your model using `summary()`
summary(age_lm)
```{r echo = FALSE}
summary(age_lm)
```

## Creating predictions using `predict()`
age_predict_df <- data.frame(earn = predict(age_lm, age_lm$earn), age = heights_df$age)
```{r echo = FALSE}
age_predict_df <- data.frame(earn = predict(age_lm, age_lm$earn), age = heights_df$age)
```

## Plot the predictions against the original data
``` {r echo = FALSE}
ggplot(data = age_lm, aes(y = earn, x = age)) +
  geom_point(color='blue') +
  geom_line(color='red', data = age_predict_df, aes(y = earn, x = age))
```

## Calculate the mean earnings
mean_earn <- mean(heights_df$earn)
```{r echo = FALSE}
mean_earn <- mean(heights_df$earn)
mean_earn
```

## Corrected Sum of Squares Total
sst <- sum((mean_earn - heights_df$earn)^2)
```{r echo = FALSE}
sst <- sum((mean_earn - heights_df$earn)^2)
sst
```

## Corrected Sum of Squares for Model
ssm <- sum((mean_earn - age_predict_df$earn)^2)
```{r echo = FALSE}
ssm <- sum((mean_earn - age_predict_df$earn)^2)
ssm
```

## Residuals
residuals <- heights_df$earn - age_predict_df$earn
```{r echo = FALSE}
residuals <- heights_df$earn - age_predict_df$earn
head(residuals)
```

## Sum of Squares for Error
sse <- sum(residuals^2)
```{r echo = FALSE}
sse <- sum(residuals^2)
sse
```

## R Squared
r_squared <- ssm / sst
```{r echo = FALSE}
ssm <- sum((mean_earn - age_predict_df$earn)^2)
sst <- sum((mean_earn - heights_df$earn)^2)
r_squared <- ssm / sst
r_squared
```

## Number of observations
n <- nrow(heights_df)
```{r echo = FALSE}
n <- nrow(heights_df)
n
```

## Number of regression parameters
p <- 2
```{r echo = FALSE}
p <- 2
p
```

## Corrected Degrees of Freedom for Model (p-1)
dfm <- p - 1
```{r echo = FALSE}
dfm <- p - 1
dfm
```

## Degrees of Freedom for Error (n-p)
dfe <- n - p
```{r echo = FALSE}
dfe <- n - p
dfe
```

## Corrected Degrees of Freedom Total:   DFT = n - 1
dft <- n - 1
```{r echo = FALSE}
dft <- n - 1
dft
```

## Mean of Squares for Model:   MSM = SSM / DFM
msm <- ssm / dfm
```{r echo = FALSE}
msm <- ssm / dfm
```

## Mean of Squares for Error:   MSE = SSE / DFE
mse <- sse / dfe
``{r echo = FALSE}
mse <- sse / dfe
mse
```

## Mean of Squares Total:   MST = SST / DFT
mst <- sst / dft
```{r echo = FALSE}
mst <- sst / dft
mst
```

## F Statistic F = MSM/MSE
f_score <- msm / mse
```{r echo = FALSE}
mse <- sse / dfe
f_score <- msm / mse
f_score
```

## Adjusted R Squared R2 = 1 - (1 - R2)(n - 1) / (n - p)
adjusted_r_squared <- 1 - (1 - r_squared) * (n - 1) / (n - p)
```{r echo = FALSE}
adjusted_r_squared <- 1 - (1 - r_squared) * (n - 1) / (n - p)
adjusted_r_squared
```

## Calculate the p-value from the F distribution
p_value <- pf(f_score, dfm, dft, lower.tail=F)
```{r echo = FALSE}
p_value <- pf(f_score, dfm, dft, lower.tail=F)
p_value
```